Instructions for COLING-2020 Proceedings

### 2020-07-10 paper/main.tex
Figures to be added (under discussion)

To generate the $\emoticon$ dataset, 
we filtered the full set of geolocated tweets so that only tweets containing one of the 80 emoticons were included,
and any duplicate tweets were removed.
Then we preprocessed each tweet by replacing all user mentions with a special token \texttt{<mention>} and all URLs with a special token \texttt{<url>} and deleting all emojis.
We decided to keep all hashtags because hashtags can contain potentially valuable emotional content.
Finally, each tweet is labelled with the emojis that were deleted from the tweet.

@@

%\cite{yang2015twitter}
\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{SemEval2018Task2} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{NTUA-SLP}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{Baziotis} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards understanding creatieve lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}

>>>>

To generate the $\emoticon$ dataset, 
we filtered the full set of geolocated tweets so that only tweets containing one of the 80 emoticons were included,
and any duplicate tweets were removed.
Then we preprocessed each tweet by replacing all user mentions with a special token \texttt{<mention>} and all URLs with a special token \texttt{<url>} and deleting all emojis.
We decided to keep all hashtags because hashtags can contain potentially valuable emotional content.
There exist a lot of tweets that contain multiple repetitions of emojis.
We address the issue similarly to how \cite{100 million tweets} did where for each unique emoji we have a separate tweet with that emoji as a label. 
For tweets containing repetitions of the same emoji; we only save one instance of it.
Finally, each tweet is labelled with the emojis that were deleted from the tweet.

@@

%\cite{yang2015twitter}
\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{SemEval2018Task2} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{NTUA-SLP}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{Baziotis} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards understanding creatieve lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}
-Figure with number of tweets per language top 10? (Written Form) Twitter Emoticon
-Accuracies for BERT model with different hyper parameters and benchmarks 
-Twitter Corona a graph similar to what I did with the nvidia sent but for the emoji's top 10 
-Figure for correlation between plutchik wheel and emoji (the one you posted on github)
-Spatial distribution of the dataset
